\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-12 learning.tex
cosmetic

% \begin{equation}
%     \operatornamewithlimits{argmin}_{A,B}\displaystyle\sum_{i=1}^{N}{\left(\x' - (A\x + B)\right)^2}
% \label{reg}
% \end{equation}

% To ease the presentation, we can rewrite the above as a homogeneous
% expression by using $\hat{\x} = [\x^T\ 1]^T$ and replacing $A$ and $B$ by the vector
% $\vec{A} = [A\ B]$. The equation~\ref{reg} now becomes
% \[
% \operatornamewithlimits{argmin}_{\vec{A}}\displaystyle\sum_{i=1}^{N}{(\x' - \vec{A}^T \hat{\x})^2}
% \]

% The solution of OLS can be analytically computed as the Moore-Penrose
% pseudo-inverse: $\vec{A} = (X^TX)^{-1}X^T X'$, where $X$ is the matrix
% representing the horizontal stacking of all $\hat{\x}$ and $X'$
% represents the stacking of all $\x'$ values.  The details can be found
% in standard texts on learning and statistics
% \cite{friedman2001elements}. Alternative methods based on gradient
% descent can also be used to find a suitable $A$ matrix.

% In this fashion, we can we can use OLS to approximate its trajectories
% of system $\System$ at fixed time step $\Delta$ by a discrete map $\x'
% = \vec{A}\hat{\x}$.

% where
% $A = \begin{bmatrix}\vec{a}_1^T \\ \vdots \\ \vec{a}_n^T
% \end{bmatrix}$ and $\vb = \begin{bmatrix}b_1 \\ \vdots \\ b_n
% \end{bmatrix}$.

% We note that linear regression tools are often able to provide an
% $n\times 1$ vector $\vec{\delta}$ of error intervals, where the
% $i^{th}$ entry of the form $[{\delta_i}_{\min},{\delta_i}_{\max}]$
% indicates the best and worst possible error in computation of the
% $i^{th}$ state in $\x'$.

% \mypara{Regression Analysis}

% In statistics, regression is the problem of finding a
% \textit{predictor}, which can suitably predict the relationship
% between the given set of observed input $\x$ and output $\y$ vectors.
% In other words, assuming that $\y$ depends on $\x$, regression
% strategies find either a parameterized or a non-parameterized
% prediction function to explain the dependence. We now discuss simple
% linear regression, which is parametric in nature and searches for an
% affine predictor. It is also called \textit{ordinary least squares}.

% \mypara{Ordinary Least Squares (OLS)}

% Let the data set be comprised of $N$ input and output pairs $(\x,
% y)$, where $\x\in\reals^n$ and $y\in\reals$. If $N>n$, which is
% the case in the current context of \textit{finding the best fit}, the
% problem is over-determined; there are more equations than
% unknowns. Hence, a single affine function cannot be found which
% satisfies the equation $\forall i\in\{1\ldots N\}. y_i = \vec{a}^T\x_i + b$. Instead, we
% need to find the `best' choice for $\vec{a}$ and $b$. This is formally
% defined using a loss function. For the case of simple linear
% regression or OLS, the loss function is the sum of squares of the
% errors in prediction.  The task is then to determine the vector of
% coefficients $\vec{a}$ and an offset constant $b$, such that the least
% square error of the affine predictor is minimized for the given data
% set.
% \begin{equation}
%     \operatornamewithlimits{argmin}_{\vec{a}, b}\displaystyle\sum_{i=1}^{N}{\left(\y_i - (\vec{a}^T\x_i + b)\right)^2}
% \label{reg}
% \end{equation}
% To ease the presentation, we can rewrite the above as a homogeneous
% expression by augmenting $\x$ by $\hat{\x} = \begin{bmatrix}\x \\ 1\end{bmatrix}$ and replacing $\vec{a}$ and $b$ by the vector
% $\vec{ab} = \begin{bmatrix}\vec{a} \\ b \end{bmatrix}$. The equation~\ref{reg} now becomes
% \[
%     \operatornamewithlimits{argmin}_{\vec{ab}}\displaystyle\sum_{i=1}^{N}{(\y_i - \vec{ab}^T \hat{\x}_i)^2}
% \]
% The solution of OLS can be analytically computed as
% \[ Ab = (X^TX)^{-1}X^T\y\]
% where $X$ is the matrix representing the horizontal stacking of all
% $\hat{\x}$.
% The details can be found in several texts on learning and statistics
% \cite{friedman2001elements}.

% Given a time invariant dynamical system $\x' = \simulate(\x, \Delta)$,
% where $\x\in\reals^n$ we can use OLS to approximate its trajectories
% at fixed time step $\Delta$ by a discrete map $\x' = A\x + \vb$, where
% $A = \begin{bmatrix}\vec{a}_1^T \\ \vdots \\ \vec{a}_n^T \end{bmatrix}$ and $\vb =
% \begin{bmatrix}b_1 \\ \vdots \\ b_n \end{bmatrix}$. This map is a
%     global relational model for the system. The data set for the
%     regression is a set of pairs $\setof{(\x,\x') | \x' =
%     \simulate(\x, \Delta)}$ and can be generated on demand. Another
%     set can be generated to compute the error $\delta$ as an interval
%     of vectors, where each element is an interval $\delta_i \in
%     [\delta_{min}, \delta_{max}]$.
%
%     Affine maps are poor
%     approximations for arbitrary non-linear functions. Hence, we use a
%     collection of affine maps to approximate the local behaviors (in
%     state-space) of the system $\simulate$. This results in a piece
%     wise approximation, as described in the next section.

% \subsection{Relational Abstractions}
% For a hybrid automaton model, they can summarize the continuous
% dynamics of each mode using a binary relation over continuous states.
% The resulting relations are timeless (independent) and hence valid for
% all time as long as the mode invariant is satisfied. The relations
% take the general form of $R(\x,\x') \bowtie 0$, where $\bowtie$
% represents one of the relational operators $=, \ge, \le, <, >$. For
% example, an abstraction that captures the monotonicity with respect to
% time for the differential equation $\dot{x} = 2$ is $x' > x$. The
% abstraction capturing the relation between the set of ODEs: $\dot{x} =
% 2$, $\dot{y} = 5$, is $5(x' - x) = 2(y' - y)$.

%%  Similar to timeless relational abstractions, time-aware relational
%%  abstractions \cite{mover2013time} construct binary relations between
%%  the current state $\x$ of the system and any future reachable state
%%  $\x'$. The difference lies with the latter also constructing relations
%%  between the current time $t$ and any future time $t'$. This is
%%  achieved by a case by case analysis of the eigen structure of the
%%  matrix $A$ (of an affine ODE). Separate abstractions are used for the
%%  case of linear systems with constant rate, real eigen values and
%%  complex eigenvalues.

>>>>

\begin{example}
\mypara{\emph{Relationalize}}: For each cell $C$, perform regression analysis on
    the respective set of trajectory segments $D(C)$, and compute a
    set of affine relations $R_{C,C'}(\x,\x')$ between $\x \in C$ and $\x'
    \in C'$ s.t., $\text{edge} (C,C') \in \scr{H}(0.1)$. Annotate
    each edge in the graph $\scr{H}(0.1)$ with the respective
    relation.

    \figref{vdp-map} shows the cells and the trajectory segments, which
    are part of the data sets constructed using the $1$-relational
    modeling. Against each cell, its unique identifier (integer
    co-ordinate) is mentioned.  Finally, \figref{vdp-graph} and
    \tabref{vdp-pwa} show the enriched graph $G^R$ with its transition
    relations. Note that self loops result when an observed trajectory
    segment has its $start$ and $end$ states in the same cell.
\end{example}

### 2017-06-12 scam.tex
cosmetic

We now give an example of a specific kind of transition system
abstraction that we can build given $\System$ and the simulation map
$\simmap_\Delta$.  We call the transition system an
$\epsilon$-precision transition system and denote it by
$\TSAbstraction{\epsilon}{\System}$.  Let $\epsilon  = 10^{-k}$, for
some positive integer $k$.  We define a quantization function
$\quant_\epsilon$ that maps a state $\contState$ in $\ContStates$ to
$10^{-k}*\lfloor \contState*10^k \rfloor$. This transformation
essentially truncates the decimal representation of the numeric value
of the state $\state$ to at most $k$ digits after the decimal point.
This function induces an equivalence relation $\contState_i
\equiv_\epsilon \contState_j$ iff $\quant_\epsilon(\contState_i) =
\quant_\epsilon(\contState_j)$.

@@

In what follows, we review the procedure
$\mathsf{ScatterAndSimulate}$($\System$,$\simmap_\Delta$,$\epsilon$)
from \cite{zutshi2014multiple} that, given the $\System$, the forward
simulation map $\simmap_\Delta$, and a precision $\epsilon$ creates an
$\epsilon$-precision transition system abstraction of $\System$.  The
essence of the procedure is a breadth-first exploration of
$\ContStates$ to build $\TSAbstraction{\epsilon}{\System}$ =
$(\Cells,\CellEdges,\CellLabelingFunction)$. It consists of the
following steps:
\begin{enumerate}
\item
Add a set of random samples from the initial set of states to a queue
(\ie some states $\contState$ at time $0$).
\item
Pop the head of the queue (say state $\contState$ at time $t$), identify
the corresponding cell by applying $\quant_\epsilon$, and add it to
$\Cells$.
\item
Obtain $\contState' = \simmap_\Delta(\contState, t, u)$. Obtain a a
fixed number of states in the neighborhood of $\contState'$, and add
$\contState'$ and these states (all time $t+\Delta$) to the queue.
\item
Add an edge between the cells corresponding to $\contState$ and
$\contState'$.
\item
Go to step 2 till either the queue is empty or a fixed number of cells
or edges is added to $\TSAbstraction{\epsilon}{\System}$.
\end{enumerate}

\begin{example}[Van der Pol Oscillator]

% \inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
% Pol: continuous trajectories. Red and green boxes indicate unsafe and
% initial sets.}{vdp-cont}
%Simulations generated using uniformly random samples are shown in
%    \figref{vdp-cont}.

\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
abstraction $\epsilon=0.2$. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

We use the Van der Pol oscillator benchmark
from~\cite{zutshi2014multiple} to demonstrate our falsification
approach. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. The
abstraction is defined by $\epsilon=0.2$, which results in an
evenly gridded state-space, where each cell is of size $0.2 \times
0.2$ units. $ScatterAndSimulate$ is then used to construct the
abstraction, using $2$ samples per cell and the time step
$\Delta = 0.1s$. The result is plotted in ~\figref{vdp-abs}.

% \mypara{Discover}: Using scatter-and-simulate, enumerate a finite number
%     of cells (vertices) and the relations (edges) of the graph
%     $\scr{H}(0.1)$. Associate the set of generated trajectory
%     segments with their respective originating cells using a map $\ds:C
%         \mapsto \setof{(\vx,\vx') |\vx \in C}$. The discovered
%     abstraction is show in \figref{vdp-abs}. The red cells
%     are unsafe and green cells are initial cells.
\end{example}

@@

We remark that our abstraction is {\em neither an overapproximation
nor an underapproximation} of the continuous-time continuous-space
reachability relation between states. The purpose of the
$\epsilon$-precision transition system is to discover falsifying
trajectories. This can be accomplished by
Algorithm~\ref{algo:s3camBMC} that uses CounterExample-Guided
Abstraction and Refinement (CEGAR).

@@

\section{An Example: Van der Pol Oscillator}
\todo{takes four iterations}
\inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Cells and
trajectory segments used by $1$-relational modeling.}{vdp-map}

% The abstraction of the hybrid dynamical system is a partitioning of
% the hybrid state space $\HybridStates$ into hyper-rectangles or cells
% $C_i \in \Cells$. The cells are pairwise disjoint $C_i \cap C_j \neq
% \emptyset$ iff $i \neq j$ and their union $\bigcup_{C_i\in\Cells}C_i$
% is the state space $\HybridStates$. The partitions over the continuous
% state space are implicitly defined using a quantization function
% $\quant_\epsilon$ parameterized by the precision $\epsilon$.  This further
% defines an equivalence relations such that $(\vx_i) \equiv (\vx_j)
% \;\text{iff}\; \quant_\epsilon(\vx_i) = \quant_\epsilon(\vx_j)$.  In other
% words, $(\vx_i) \in C_i \; \text{iff} \; C_i = \quant_\epsilon(\vx_i)$. The
% abstraction can be interpreted as a graph and explored using fixed
% time $(\Delta\in\Reals^+)$ relations obtained using
% $\simulate(\vx)$~\footnote{$\simulate(\vx)$ is a fixed
% parameterization of $\mathsc{sim}(\vx,\Delta)$}.
%
% % Such an abstraction is defined by partitioning the
% % state-space of the system using a grid, and hence each abstract state
% % is a hyper-rectangle. The relations between abstract states are
% % obtained by suitably lifting $(\vx,\vx') \in\reach{t,u}$. Considering
% % the abstract states as vertices of a graph and the relations as edges
% % between nodes, the problem of finding an abstract counter-example
% % (CEx) can be cast as finding a path in the graph. Such an abstraction
% % can be explored on-the-fly by enumerating the abstract relations
% % between a pair of states.
%
% \mypara{A discrete abstraction} over a continuous space uses relations
% to describe the behavior of the system over time. Such relations
% abstract the underlying dense-time trajectories of the given dynamical
% system to a transition system.

% relation between concrete states, and concrete
% paths can no longer be constructed directly. Instead, search
% procedures like Counter-Example Guided Refinement (CEGAR) must be used
% to find concrete paths. In general, such search techniques are based
% on refinement of the state-space and exponential with respect to
% computational resources and memory. As an alternative, we introduce
% data driven `enrichment' of abstractions to approximate the concrete
% relations underlying the abstract relations.  Specifically, we use
% linear regression to compute affine maps associated with the relations
% between two abstract states. We then show how associating the computed
% maps with the relations transforms a discrete abstraction into a PWA
% transition system.

% The abstraction of the hybrid dynamical system is a a
% partitioning of the combined state-input space $\HybridStates \times
% \Inputs$ into hyper-rectangles or cells $C_i \in \Cells$. The cells are
% pairwise disjoint $C_i \cap C_j \neq \emptyset$ iff $i \neq j$ and
% their union $\bigcup_{C_i\in\Cells}C_i$ is the state-input
% space $\HybridStates \times \Inputs$. The partitions over
% the continuous input-state space are implicitly defined using a quantization
% function $\quant_\epsilon$ parameterized by the precision $\epsilon$.
% This further defines an equivalence relations such that
% \[
%     (\vx_i, \vu_i) \equiv (\vx_j, \vu_j) \;\text{iff}\; \quant_\epsilon(\vx_i,
%     \vu_i) = \quant_\epsilon(\vx_j, \vu_j)
% \]
% In other words, $(\vx_i, \vu_i) \in C_i \; \text{iff} \; C_i =
% \quant_\epsilon(\vx_i, \vu_i)$.

% \begin{definition}[Graph Abstraction]
%     The quantization function $\quant_\epsilon$ induces a DAG on the discrete
%     abstraction given by a graph $G(V, E)$, where each vertex
%     corresponds to a cell $V_i = C$, and an edge exists between two
%     cells $(C, C') \in E_i$ iff there exist state-input pairs
%     $(\vx,\vu) \in C$, $(\vx', \vu) \in C'$ such that $\vx' =
%     \simulate(\vx, \vu )$.
% \end{definition}

% \begin{definition}[Graph Abstraction]
%     The quantization function $\quant_\epsilon$ induces a directed acyclic
%     graph (DAG) on the discrete
%     abstraction given by a graph $G(V, E)$, where each vertex
%     corresponds to a cell $V_i = C$, and an edge exists between two
%     cells $(C, C') \in E_i$ iff there exist state-input pairs
%     $(\vx) \in C$, $(\vx') \in C'$ such that $\vx' =
%     \simulate(\vx)$.
% \end{definition}
%
%
%
% Given a numerical simulator $\simulate$ and an initial abstraction
% defined by a quantization function $\quant_\epsilon$ and a time step
% $\Delta$, we pick samples and simulate them to explore the abstraction
% on the fly to obtain a graph $G$, which has a finite number of
% abstract states $C$ (or cells) and edges $(C,C')$ iff $C
% \areach{\Delta} C'$.

% \begin{definition}[Abstract State Graph]. Let ∆ > 0 be a fixed time
%     step. The abstract state graph H(∆) for time step ∆ is defined by
%     the set of vertices C, and edges (Ci, Cj ) whenever Ci ∆ Cj . Let
%     C0 denote the collection of initial cells in C, i.e., cells Ci
%     such that Ci ∩ X0 6= ∅. Further, let Cu denote the set of unsafe
%     cells, or cells Cj such that there is a state xj ∈ Cj that reaches
%     an unsafe state y ∈ Xf within time 0 ≤ tj < ∆. The abstraction
% H(∆) is given by D C, ∆ , C0, Cu E .  \end{definition}

% As
% Instead of using a CEGAR like loop (used in~\cite{zutshi2014multiple}),
% we use the generated trajectories to learn quantitative models
% describing the local behavior of the system. These models are defined
% by a set of relations $R \subseteq \HybridStates \times \HybridStates$
% for each edge of the reachability graph. In the next section, we
% summarize this idea.

% \subsection{Enriched Abstraction}
%
% \input{figs/segtraj_rel_enriched.tex}
%
% Recall that each edge $(C,C')$ of the graph $G$ denotes an observed
% trajectory between the respective cells. The graph abstraction $G$
% only states that there exists a state $\x \in C$ from which the system
% can evolve to a future state $\x' \in C'$. To increase the precision,
% iterative refinement of the abstraction by state splitting was
% proposed in~\cite{zutshi2014multiple}. Due to the curse of
% dimensionality, state splitting is not scalable. Instead, we propose
% an `enrichment' $G^R$ of $G$ by computing a set of local relations
% $R_{(C,C')}(\x,\x')$ for every edge $(C,C')$, which
% non-deterministically describe relations between $\x \in C$ and $\x'
% \in C'$. This is illustrated in \figref{enriched-edge}.
% %(compare with \figref{segtraj}).
%
% The enriched graph $G^R$ captures the underlying local forward
% dynamics describing the evolution of the system in each abstract
% state. We represent the dynamics using an affine model with an
% interval error. Such a model can either be approximated using learning
% methods or computed as a sound (over) approximation using reachability
% set computation methods. Because we assume black box semantics, we
% only present the former. Using regression analysis on a witnessed
% trajectory between two cells, we compute an approximate discrete map
% along with an error estimate.  Moreover, using the simulation function
% $\simulate$, additional trajectories (or data) can be generated if
% required. The data can be separated into a training set and testing
% set to compute the map and the error respectively.
%
% %The latter case can be explored if
% %the symbolic dynamics of the system are known. A tool like
% %\flowstar~\cite{chen2013flow} can be used to find the reachable set
% %map.
%
% Observe that $G^R$, a directed reachability graph, is rich enough to
% search for concrete behaviors in the system. We call it a time
% parameterized PWA relational abstraction. It can be interpreted as an
% infinite state discrete transition system, and we can use
% off-the-shelf bounded model checkers to find concrete violations of a
% given safety property, and even other temporal properties.

% \begin{figure}[!htbp]
% \begin{center}
% \tikzstyle{line} = [thick]
% \tikzstyle{arw} = [->, thick,>=stealth,shorten <=2pt, shorten >=2pt]
% \tikzstyle{block} = [rectangle, minimum width=0.5cm, minimum height=1.0cm, text centered, draw=black, align=center]%, fill=blue!25]
% \begin{tikzpicture}[scale=1.0, on grid, auto]
%
%     \node (G) at (-4,0) {$G$};
%     \node (GR) at (0,0) {$G^R$};
%     \node (CEX) at (4,0) {$CEx$};
%
%     \node (enrich) [block] at (-2, 0) {\scriptsize Enrich using \\ \scriptsize affine  maps};
%     \node (BMC) [block] at (2, 0) {\scriptsize Find CEx \\ \scriptsize using BMC};
%
%     %\node[align=center] at (0, 0) {\scriptsize Enrich using \\ \scriptsize Regression \\ \scriptsize(OLS)};
%
%     %\draw [line] (-2.0,-0.5) rectangle (-1.0,0.5);
%     \draw[arw] (G.east) -- (enrich.west);
%     \draw[arw] (enrich.east) -- (GR.west);
%     \draw[arw] (GR.east) -- (BMC.west);
%     \draw[arw] (BMC.east) -- (CEX.west);
%
% \end{tikzpicture}
% \end{center}
% \vspace*{-.3cm}
% \caption{Finding counter-examples (CEx) in a graph abstraction using PWA models.}
% \label{fig:overview}
% \vspace*{-.3cm}
% \end{figure}

>>>>

We now give an example of a specific kind of transition system
abstraction that we can build given $\System$ and the simulation map
$\simmap_\Delta$.  We call the transition system an
$\epsilon$-precision transition system ($\epsilon$-TS for short) and
denote it by $\TSAbstraction{\epsilon}{\System}$.  Let $\epsilon  =
10^{-k}$, for some positive integer $k$.  We define a quantization
function $\quant_\epsilon$ that maps a state $\contState$ in
$\ContStates$ to $10^{-k}*\lfloor \contState*10^k \rfloor$. This
transformation essentially truncates the decimal representation of the
numeric value of the state $\state$ to at most $k$ digits after the
decimal point.  This function induces an equivalence relation
$\contState_i \equiv_\epsilon \contState_j$ iff
$\quant_\epsilon(\contState_i) = \quant_\epsilon(\contState_j)$.

@@

In what follows, we review the procedure
$\mathsf{ScatterAndSimulate}$($\System$,$\simmap_\Delta$,$\epsilon$)
from \cite{zutshi2014multiple} that, given the $\System$, the forward
simulation map $\simmap_\Delta$, and a precision $\epsilon$ creates an
$\epsilon$-TS abstraction of $\System$.  The
essence of the procedure is a breadth-first exploration of
$\ContStates$ to build $\TSAbstraction{\epsilon}{\System}$ =
$(\Cells,\CellEdges,\CellLabelingFunction)$. It consists of the
following steps:
\begin{enumerate}[leftmargin=1em,labelsep=1em,label={\arabic*.}]
\item
Add a set of random samples from the initial set of states to a queue
(\ie some states $\contState$ at time $0$).
\item
Pop the head of the queue (say state $\contState$ at time $t$), identify
the corresponding cell by applying $\quant_\epsilon$, and add it to
$\Cells$. 
\item
Obtain $\contState' = \simmap_\Delta(\contState, t, u)$. Obtain a a
fixed number of states in the neighborhood of $\contState'$, and add
$\contState'$ and these states (all time $t+\Delta$) to the queue. 
\item
Add an edge between the cells corresponding to $\contState$ and 
$\contState'$.
\item
Go to step 2 till either the queue is empty or a fixed number of cells
or edges is added to $\TSAbstraction{\epsilon}{\System}$.
\end{enumerate}

\inclfig[width=0.95\linewidth]{vdp_cont_traces.pdf}{Van der
Pol: continuous trajectories. Red and green boxes indicate unsafe and
initial sets.}{vdp-cont}
\inclfig[width=0.95\linewidth]{vdp_abs.pdf}{The discovered
$0.2$-TS abstraction. Red cells are unsafe cells and green cells are
initial cells.}{vdp-abs}

\begin{example} 
We now describe $\epsilon$-TS abstraction using the Van der Pol
oscillator benchmark from~\cite{zutshi2014multiple}. Simulations
generated using uniformly random samples are shown in
\figref{vdp-cont}. We want to check the property $P_3$, indicated by
the red box, given the initial set indicated by the green box. We
consider the $\epsilon$-TS abstraction defined by the quantization
function $\quant_{0.2}(\x)$. This results in an evenly gridded
state-space, where each cell is of size $0.2 \times 0.2$ units.
$\mathsf{ScatterAndSimulate}$ is then used to construct
$\TSAbstraction{0.2}{\System}$ using $2$ samples per cell and a time
step of $\Delta = 0.1s$. The complete process follows.  The
$\epsilon$-TS abstraction thus discovered is shown in
\figref{vdp-abs}. The red cells are unsafe and green cells are initial
cells.
\end{example}

% \mypara{Abstract}: Assume an implicit abstraction using the quantization
%         function $\quant_{\epsilon=0.2}(\x)$. The corresponding reachability
%     graph is $\scr{H}(\Delta=0.1)$.
% 
% \mypara{Discover}: Using scatter-and-simulate, enumerate a finite number
%     of cells (vertices) and the relations (edges) of the graph
%     $\scr{H}(0.1)$. Associate the set of generated trajectory
%     segments with their respective originating cells using a map $\ds:C
%         \mapsto \setof{(\vx,\vx') |\vx \in C}$.

@@

We remark that our abstraction is {\em neither an overapproximation
nor an underapproximation} of the continuous-time continuous-space
reachability relation between states. The purpose of the $\epsilon$-TS
is to discover falsifying trajectories. This can be accomplished by
Algorithm~\ref{algo:s3camBMC} that uses CounterExample-Guided
Abstraction and Refinement (CEGAR).

@@

% \subsection{Example: Van der Pol Oscillator}
% \todo{Takes 4 iterations}
% \inclfig[width=0.90\linewidth]{vdp_disc_map.pdf}{Refinement of
% $\epsilon$-TS.}{vdp-map}
%
